Index measures for oak decline severity using phenotypic descriptors

### 2020-02-07 manuscript/manuscript.Rmd
small proofing changes

1. Institute of biological, environmental and rural sciences, Aberystwyth University, Aberystwyth, SY23 3DA, UK

2. Centre for Forestry and Climate Change, Forest Research, Alice Holt Lodge, Farnham GU 4LH, UK

>>>>

^1^ Institute of Biological, Environmental and Rural Sciences, Aberystwyth University, Aberystwyth, SY23 3DA, UK

^2^ Centre for Forestry and Climate Change, Forest Research, Alice Holt Lodge, Farnham GU 4LH, UK
